Fusion Moves for Correlation Clustering

### 2014-11-12 paper/egpaper_for_review.tex
fixed typo in param choise
exp

@@

\subsection{Social Networks and Network Clustering}
An application for large scale correlation clustering are social networks.
We consider two of those networks from the Stanford Large Network Dataset Collection\footnote{\url{http://snap.stanford.edu/data/index.html}}.
Both networks are given by weighted directed graphs with edge weights $-1$ and $1$. 
%
The first network is called \emph{Epinions}. 
This is who-trust-whom online social network of a a general consumer review site Epinions.com. 
Each directed edge $a\to b$ indicated that user $a$ trusts  or does not trust user $b$ by a  positive or negative edge-weight, respectively.
The network contains $131828$ nodes and $841372$ edges from which $85.3\%$ are positively weighted.
%
The second network is called \emph{Slashdot}. 
Slashdot is a technology-related news website know for its specific user community. 
In 2002 Slashdot introduced the Slashdot Zoo feature which allows users to tag each other as friends or foes. 
The network was obtained in November 2008 and contains $77350$ nodes and $516575$ edges from which $76.73\%$ are positively weighted.

We consider the problem to cluster this graphs such that positively weighted edges ($E^+_{\to}$) link inside and negatively weighted edges ($E^-_{\to}$) between clusters.
In other words friends and people who trust each other should be in the same segment and foes and non-trusting people in different clusters.
% 
To compensate the high impact of nodes with high degree we can normalize the edge weights such that each person has the same impact to the overall network, by enforcing.
\begin{align}
  \sum_{i\to j \in E_{\to}} |w_{i\to j}| &= 1&\forall i\in V, deg^{\textrm{out}}(i)\geq 1 
\end{align}
We define the following energy function
\begin{align}
 J(y) &= \sum_{i\to j \in E^+_{\to}} y_{ij}\cdot w_{i \to j} +  \sum_{i\to j \in E^-_{\to}} (y_{ij}-1)\cdot w_{i \to j} \nonumber\\
      &= \sum_{ij \in E} y_{ij}\cdot \underbrace{(w_{i \to j}+w_{j \to i})}_{w_{ij}} + \textrm{const}
\end{align}
which is zero if the given partitioning does not violated any relation and larger otherwise.

As shown in Fig.~\ref{fig:anytime} (g,h) CCFusion provides for the first minutes the best results.
Only CGC and HC-CGC are able to find better solutions after more then 1000 seconds.
MC-I and MC-R can even not be applied on such large problems.
We belief that with better proposal generators, which are more suited for such network problems,
we can improve CCFusion. One candidate for such a generated would be a scalable method for the 
PIVOT algorithm.

As another example for network clustering we use the modularity-clustering models from~\cite{kappes_2014_benchmark_arxiv} which are small but fully connected.
Although, CCFusion and the used parameters was not designed and chosen for this type of problem, it performs on par to competitive methods. 
Especially is does a better job than MC-I as shown in Fig.~\ref{fig:anytime} (i)

\subsection{2D and 3D Image Segmentation}
To segment images or volumes into a previously
unknown number of clusters, correlation clustering
has been used~\cite{andres_2011_iccv,kroeger_2012_eccv}.

@@

{\color{red}\textbf{TODO: Discussion}}

\begin{table}[H]
   \tiny
   \centering
   \caption{Datasets used for evaluation}
   \label{tab:instance_sizes}
   \begin{tabular}{llllc}
      \toprule
         Dataset          &     \#Nodes     & \#Edges  & \#Instances  & Planar        \\ 
      \midrule 
         image-seg        &     156-3764        & ???              & 100          & $\bullet$    \\ 
         knott-150        &     572-972         & ???              & 2            & $\times$ \\
         knott-300        &     3846 - 5896     & ???              & 2            & $\times$ \\
         knott-450        &     15150-17070     & ???              & 2            & $\times$ \\
         knott-550        &     27286 - 31249   & ???              & 2            & $\times$ \\
         3d-seg           &     101220          & ???              & 1            & $\times$ \\
         socialnets       &     77350 - 131828  & 516575 - 841372  & 2            & $\times$ \\  
      \bottomrule
   \end{tabular}
\end{table}

\begin{table}[H]
   \tiny
   \centering
   \caption{Evaluation of Variation of Information (VI) for datasets with available ground-truth.}
   \label{tab:eval}
   \begin{tabular}{lllllll}
      \toprule
         Dataset          &  image-seg   & knott-3d-150 & knott-3d-300   & knott-3d-450 & knott-3d-550 &3d-seg\\
      \midrule 
         PIVOT-BOEM       &   $ 4.9633$  &    $ 2.9936$ &       --       &              &              &  --\\ 
         HC               &   $ 2.5967$  &    $ 1.5477$ &    $ 2.3513$   &    $ 2.9155$ &              & $       2.8395$\\
         HC-CGC           &   $ 2.5164$  &    $ 0.9052$ &    $ 1.7636$   &    $ 2.2256$ &              & $       1.7603$ \\
         CGC              &   $ 2.5247$  &    $ 0.9267$ &    $ 1.8822$   &    $ 2.3104$ &              & $       6.8908$ \\
         KL               &   $ 2.6432$  &    $ 2.0648$ &    $ 4.1318$   &    $ 4.9270$ &              & $       7.1057$\\
         FUSION           &      --      &    $ 2.8787$ &    $ 4.0744$   &    $ 4.6616$ &              & $       6.5366$ \\
         MC-R             &   $ 2.5471$  &    $ 0.9178$ &    $ 1.6369$   &    $ 2.8710$ &              & $       6.5058$\\   
         MC-I             &   $ 2.5367$  & $\bf 0.9063$ & $\bf 1.6352$   & $\bf 2.0037$ &              & $       4.3319$\\  
         FusionCC-HC-MC   &   $ 2.5319$  &    $ 0.9629$ &    $ 1.6516$   &    $ 2.0801$ &              & $\bf    1.3347$ \\  
         FusionCC-HC-CGC  &$\bf 2.4961$  &    $ 0.9679$ &    $ 1.7673$   &    $ 2.3809$ &              & $       2.1347$ \\  
         FusionCC-WS-MC   &   $ 2.5340$  &    $ 0.9629$ &    $ 1.6742$   &    $ 2.0739$ &              & $\bf    1.3334$ \\  
         FusionCC-WS-CGC  &   $ 2.5192$  &    $ 1.0585$ &    $ 2.1344$   &    $ 2.7487$ &              & $       3.3514$ \\      
      \bottomrule
   \end{tabular}
\end{table}

>>>>

An overview of the used datasets is given in Tab.~\ref{tab:instance_sizes} and described in detail in Sec.\ref{sec:nets} and \ref{sec:imseg}.

\begin{table}[th]
   \tiny
   \centering
   \caption{Datasets used for evaluation}
   \label{tab:instance_sizes}
   \begin{tabular}{llllc}
      \toprule
         Dataset          &     \#Nodes     & \#Edges  & \#Instances  & Planar        \\ 
      \midrule 
         image-seg        &     156-3764        & ???              & 100          & $\bullet$    \\ 
         knott-150        &     572-972         & ???              & 2            & $\times$ \\
         knott-300        &     3846 - 5896     & ???              & 2            & $\times$ \\
         knott-450        &     15150-17070     & ???              & 2            & $\times$ \\
         knott-550        &     27286 - 31249   & ???              & 2            & $\times$ \\
         3d-seg           &     101220          & ???              & 1            & $\times$ \\
         socialnets       &     77350 - 131828  & 516575 - 841372  & 2            & $\times$ \\  
      \bottomrule
   \end{tabular}
\end{table}

@@

\subsection{Social Networks and Network Clustering}\label{sec:nets}
An application for large scale correlation clustering are social networks.
We consider two of those networks from the Stanford Large Network Dataset Collection\footnote{\url{http://snap.stanford.edu/data/index.html}}.
Both networks are given by weighted directed graphs with edge weights $-1$ and $1$. 
%
The first network is called \emph{Epinions}. 
This is who-trust-whom online social network of a a general consumer review site Epinions.com. 
Each directed edge $a\to b$ indicated that user $a$ trusts  or does not trust user $b$ by a  positive or negative edge-weight, respectively.
The network contains $131828$ nodes and $841372$ edges from which $85.3\%$ are positively weighted.
%
The second network is called \emph{Slashdot}. 
Slashdot is a technology-related news website know for its specific user community. 
In 2002 Slashdot introduced the Slashdot Zoo feature which allows users to tag each other as friends or foes. 
The network was obtained in November 2008 and contains $77350$ nodes and $516575$ edges from which $76.73\%$ are positively weighted.

We consider the problem to cluster this graphs such that positively weighted edges ($E^+_{\to}$) link inside and negatively weighted edges ($E^-_{\to}$) between clusters.
In other words friends and people who trust each other should be in the same segment and foes and non-trusting people in different clusters.
% 
To compensate the high impact of nodes with high degree we can normalize the edge weights such that each person has the same impact to the overall network, by enforcing.
\begin{align}
  \sum_{i\to j \in E_{\to}} |w_{i\to j}| &= 1&\forall i\in V, deg^{\textrm{out}}(i)\geq 1 
\end{align}
We define the following energy function
\begin{align}
 J(y) &= \sum_{i\to j \in E^+_{\to}} y_{ij}\cdot w_{i \to j} +  \sum_{i\to j \in E^-_{\to}} (y_{ij}-1)\cdot w_{i \to j} \nonumber\\
      &= \sum_{ij \in E} y_{ij}\cdot \underbrace{(w_{i \to j}+w_{j \to i})}_{w_{ij}} + \textrm{const}
\end{align}
which is zero if the given partitioning does not violated any relation and larger otherwise.
We name this two datasets \emph{social nets} and \emph{normalized social nets}.

As shown in Fig.~\ref{fig:anytime}(g,h) CCFusion provides for the first minutes the best results.
Only CGC and HC-CGC are able to find better solutions after more then 1000 seconds.
MC-I and MC-R can even not be applied on such large problems.
We belief that with better proposal generators, which are more suited for such network problems,
we can improve CCFusion. One candidate for such a generated would be a scalable method for the 
PIVOT algorithm.

As another example for network clustering we use the \emph{modularity-clustering} models from~\cite{kappes_2014_benchmark_arxiv} which are small but fully connected.
Although, CCFusion and the used parameters was not designed and chosen for this type of problem, it performs on par to competitive methods. 
Especially is does a better job than MC-I as shown in Fig.~\ref{fig:anytime}(i)

\subsection{2D and 3D Image Segmentation}\label{sec:imseg}
To segment images or volumes into a previously
unknown number of clusters, correlation clustering
has been used~\cite{andres_2011_iccv,kroeger_2012_eccv}.

@@

For image-seg CCFusion is faster than competitive methods, \cf Fig.~\ref{fig:anytime}(a).
The variation of information~\cite{} (VI) of the CCFusion methods is also best, \cf Tab.~\ref{tab:eval}.
Proposals by EHC seemed to be a bit better than WS-based ones.

For the knott-datasets similar holds. With increasing problem size CCFusion-HC-MC and CCFusion-WS-MC have a better performance compared to competitive methods, \cf Fig.~\ref{fig:anytime}(b-e).
Also in terms of VI they are only slightly worse than the global optimal solution found by MC-I.
The initialization of CGC by HC denoted by HC-CGC also improves the performance compared to native CGC.
For the largest 3D volume seg-3d, HC-CGC gives the first good solution, \cf  Fig.~\ref{fig:anytime}(f).
However, after a view minutes  CCFusion-HC-MC and CCFusion-WS-MC give much better results and also overall best in terms of energy and VI, \cf Tab.~\ref{tab:eval}.

Pure HC, Fusion and PIVOT-BOEM do not give useful results on any dataset.

\begin{table}[th]
   \tiny
   \centering
   \caption{Evaluation of Variation of Information (VI) for datasets with available ground-truth.}
   \label{tab:eval}
   \begin{tabular}{lllllll}
      \toprule
         Dataset          &  image-seg   & knott-3d-150 & knott-3d-300   & knott-3d-450 & knott-3d-550 &3d-seg\\
      \midrule 
         PIVOT-BOEM       &   $ 4.9633$  &    $ 2.9936$ &       --       &              &              &  --\\ 
         HC               &   $ 2.5967$  &    $ 1.5477$ &    $ 2.3513$   &    $ 2.9155$ &              & $       2.8395$\\
         HC-CGC           &   $ 2.5164$  &    $ 0.9052$ &    $ 1.7636$   &    $ 2.2256$ &              & $       1.7603$ \\
         CGC              &   $ 2.5247$  &    $ 0.9267$ &    $ 1.8822$   &    $ 2.3104$ &              & $       6.8908$ \\
         KL               &   $ 2.6432$  &    $ 2.0648$ &    $ 4.1318$   &    $ 4.9270$ &              & $       7.1057$\\
         FUSION           &      --      &    $ 2.8787$ &    $ 4.0744$   &    $ 4.6616$ &              & $       6.5366$ \\
         MC-R             &   $ 2.5471$  &    $ 0.9178$ &    $ 1.6369$   &    $ 2.8710$ &              & $       6.5058$\\   
         MC-I             &   $ 2.5367$  & $\bf 0.9063$ & $\bf 1.6352$   & $\bf 2.0037$ &              & $       4.3319$\\  
         FusionCC-HC-MC   &   $ 2.5319$  &    $ 0.9629$ &    $ 1.6516$   &    $ 2.0801$ &              & $\bf    1.3347$ \\  
         FusionCC-HC-CGC  &$\bf 2.4961$  &    $ 0.9679$ &    $ 1.7673$   &    $ 2.3809$ &              & $       2.1347$ \\  
         FusionCC-WS-MC   &   $ 2.5340$  &    $ 0.9629$ &    $ 1.6742$   &    $ 2.0739$ &              & $\bf    1.3334$ \\  
         FusionCC-WS-CGC  &   $ 2.5192$  &    $ 1.0585$ &    $ 2.1344$   &    $ 2.7487$ &              & $       3.3514$ \\      
      \bottomrule
   \end{tabular}
\end{table}
